AHABus \& FCORE:\\Modular Bus for High-Altitude Balloon Missions

### 2017-04-12 chapters/04-results.tex
Add GNSS task
pre-discussion

\section{Observed Issues}

\subsection{Radio Communications}

@@

\subsection{Payload Bus}

>>>>

\section{General Observations}

Overall, the \acrshort{ahabus} prototype met expectations and performed well.
While some minor issues were encountered during the initial round of testing,
both endpoints of the platform – flight platform and ground segment – functioned
well enough that the next round of testing (range and flight tests) would be
achievable.

\subsection{Radio Communications}
\label{ssec:results-rtx}

@@

\subsection{Payload Bus}
\label{ssec:results-bus}

### 2017-04-12 chapters/05-discussion.tex
pre-discussion

>>>>

While the platform proved reliable and would be well suited for scientific
missions, where most of the generated telemetry is numerical measurements, it
might be less adequate for student missions where most users would expect to
transmit more data, like real-time pictures: the packets size limit
(\SI{420}{\byte}) would make transmitting any reasonably-sized image impossible.
This issue could potentially be solved by adding time division algorithms other
than the one presented in section \ref{ssec:conf-file}.
